%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {Siddhartha Banerjee},
  pdfkeywords = {robotics, human-robot interaction, artificial intelligence},
  pdftitle = {Siddhartha Banerjee: Resume},
  pdfsubject = {Resume},
  pdfpagemode = UseNone
}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\par\hfill{\scriptsize\color{gray}Last updated on 1st Feb 2025}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Siddhartha}{Banerjee}{ \urlstyle{same}\href{https://banerjs.github.io}{banerjs.github.io} | \href{mailto:banerjs.sid@gmail.com}{banerjs.sid@gmail.com} | +1.203.435.1923
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Georgia Inst. of Tech.}
\descript{Ph.D. in Robotics}
\location{May 2021 | Atlanta, GA}
Title: Facilitating Reliable Autonomy with Human-Robot Interaction \\
Advised by Dr. Sonia Chernova
\sectionsep

\subsection{Yale University}
\descript{B.S. in Electrical Engineering/Computer Science}
\location{May 2013 | New Haven, CT}
Distinction in Major \\
GPA: 3.7 / 4.0

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/banerjs}{\bf banerjs} \\
LinkedIn://  \href{https://www.linkedin.com/in/banerjs}{\bf banerjs} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Artificial Intelligence {\scriptsize (Student \& TA)} \\
Deep Learning \\
Linear Systems \& Control \\
Nonlinear Systems \\
Human-Robot Interaction {\scriptsize (Student \& TA)} \\
Human-Computer Interaction \\
Evaluation of Human Integrated Systems \\
\sectionsep

\subsection{Undergraduate}
Intro to VLSI System Design \\
Systems \& Control \\
Science of Complex Systems \\
Systems Programming \\
Design \& Analysis of Algorithms \\
Intelligent Robotics \\
Computational Vision \\
Database Systems \\
Mobile Computing \& Wireless Networks \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Programming
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Programming}
\subsection{Languages}
Python \textbullet{} C++ \textbullet{} C \textbullet{} Java \textbullet{} C\# \\
MATLAB \textbullet{} Javascript \textbullet{} R \textbullet{} SQL
\sectionsep

\subsection{Frameworks}
ROS \textbullet{} PyTorch \textbullet{} scikit-learn \textbullet{} Jupyter \\
ReactJS \textbullet{} NextJS \textbullet{} NestJS \textbullet{} Django \\
Docker \textbullet{} Ansible \textbullet{} Terraform \\
gRPC \textbullet{} SocketIO \textbullet{} WebRTC (basic)

% \subsection{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work Experience}
\runsubsection{Diligent Robotics}
\descript{| Lead Robotics Software Engineer }
\location{May 2018 - August 2018, January 2021 - December 2024 | Austin, TX}
\vspace{0.3cm}
\begin{tightemize}
\item Led a team of 9 engineers on cloud and robot applications; planned quarterly roadmaps, oversaw sprint progress, and conducted monthly architecture reviews with the CTO on projects, vendors, tech debt, and system health.
\item Built remote robot management software, growing from 1 to 100+ robots across 30+ clients; enabled new hospital workflows and integrations, boosting adoption; improved reliability by cutting average operator intervention time to <30s and scaling operator-to-robot ratio to >1:7.
\item Contributed across the full software stack (robot, cloud, embedded); primary developer and maintainer of remote operations, task execution, and scheduling; integrated new systems, onboarded vendors, incorporated new hardware, and supported client implementations.
\end{tightemize}
\sectionsep

\runsubsection{Microsoft}
\descript{| Research Intern }
\location{May 2017 - August 2017 | Seattle, WA}
\begin{tightemize}
\item Contributed to the Situated Interaction Group's development of agents for seamless human interaction in real-world environments.
\item Configured a robot to update activity recognition models in-the-wild; evaluated different person and pose detection algorithms on the robot as a first step.
\end{tightemize}
\sectionsep

\runsubsection{Redfin}
\descript{| Software Engineer II }
\location{July 2013 – June 2015 | Seattle, WA}
% \vspace{0.3cm}
\begin{tightemize}
\item Enhanced and maintained ETL pipelines for house listing data, driving Redfin’s market expansion by >120\% (2013–2015); integrated GIS data from multiple providers and built tools for data disambiguation.
\item Aggregated housing data by region to enhance user experience and reduce historical tech debt.
\end{tightemize}
\sectionsep

% \runsubsection{Microsoft}
% \descript{| Hardware Verification Intern }
% \location{May 2012 – August 2012 | Mountain View, CA}
% % \vspace{0.3cm}
% \begin{tightemize}
% \item VLSI hardware verification and testing for the Xbox One
% \item Used waveform analysis and BIOS Kernel Developer Specifications to test a System-on-Chip
% \end{tightemize}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS & Leadership
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards \& Leadership}
\begin{tabular}{rll}
2019 & Panel Chair & HRI Pioneers Workshop \\
2017--2018 & President & Georgia Tech RoboGrads \\
% 2016--2017 & Social Chair & Georgia Tech RoboGrads \\
2014 & Employee of Quarter & Redfin \\
% 2012--2013 & Team Mentor & Yale Formula Hybrid FSAE Team \\
2011 & Fellow & Yale Entrepreneurial Institute Summer Fellowship \\
2011--2012 & Vice-President & Yale Formula Hybrid FSAE Team
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     NOTABLE PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Notable Publications}
\renewcommand\refname{\vskip -0.8cm} % Couldn't get this working from the .cls file
\bibliographystyle{IEEEtran}
\bibliography{../_bibliography/resume}
\nocite{*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SELECT PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Select Projects}
\runsubsection{FetchIt! Challenge}
\descript{| Robotics Competition}
\location{Summer 2019 | ICRA}
Developed robot software to complete a mobile manipulation challenge at the ICRA 2019 FetchIt! Challenge hosted by Fetch Robotics. The team placed first, winning a Fetch mobile manipulator robot.
\sectionsep

\runsubsection{Yale Formula Hybrid FSAE}
\descript{| Student Organization}
\location{2009 - 2013 | Yale}
Designed and built formula style gas-electric hybrid cars to compete nationally. Team won several awards including Best Hybrid Car (2013), Ford Efficiency (2013), Chrysler Innovation (2013), \& GM Best Engineered Hybrid System (2010, 2013)
\sectionsep

\end{minipage}
\end{document}
